---
title: "InfluenceMetric"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{InfluenceMetric}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

```{r setup}
library(InfluenceMetric)
```

The InfluenceMetric package calculates various distance measures (Cook's Distance, DFFITS, or Hadi's Influence Measure) to assess the influence of individual points in a linear regression model. Users can either return the calculated values or generate plots for visual analysis.

# Example 1: Cook's Distance 

In this example, we calculate and plot Cook's Distance for a simple linear model.
```{r}
# Set seed for reproducibility
set.seed(123)

# Generate random data
n <- 50  # number of observations
p <- 2   # number of predictors (excluding intercept)

X <- matrix(rnorm(n * p), n, p)
y <- rnorm(n)

# Add intercept term to the design matrix
X <- cbind(1, X)

# Fit linear model
model <- lm(y ~ X - 1)

# Plot Cook's Distance
influence_diagnostics_plot(model, measure = "cooks_distance", return_type = "plot", X, y)
```

Cook's Distance helps identify influential observations that significantly affect the estimated regression coefficients. Points with high Cook's Distance values may indicate outliers or leverage points that could disproportionately influence the model.

# Example 2: DFFITS values

Next, we calculate and return the DFFITS values, which measure the impact of each observation on the fitted values.
```{r}
# Return DFFITS values
dffits_values <- influence_diagnostics_plot(model, measure = "dffits", return_type = "measure", X, y)

# Print the first few DFFITS values
head(dffits_values)
```

DFFITS is particularly useful for identifying observations that significantly change the predicted values. Observations with DFFITS values greater than a certain threshold (often 2 * sqrt(p/n)) are considered influential.

# Example 3: Hadi's Influence Measure

Finally, we demonstrate how to calculate and plot Hadi's Influence Measure.

```{r}
# Plot Hadi's Influence Measure
influence_diagnostics_plot(model, measure = "hadis_influence", return_type = "plot", X, y)
```

Hadi's Influence Measure considers both the predictor and response variables to assess the overall influence of each observation. It is especially useful for detecting outliers in the X-space.
